Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-09 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Juan Julián Merelo Guervós <jjmerelo@gmail.com>

% The Use of Mobile Instant Messaging (MIM) Platforms in Higher Education
The widespread and rapid adoption of free Mobile Instant Messaging
(MIM) tools/platforms such as WhatsApp, Telegram, WeChat and Facebook
Messenger stems from their simplicity, ease of use and multi-modality
(i.e. video, audio, text) \cite{tang2017mobile}. Using these tools in
higher education facilitates the delivery of personalized learning
that occurs anytime anywhere, and promotes collaborative learning
experiences and group discussions \cite{panah2020study}.

>>>>

% The Use of Mobile Instant Messaging (MIM) Platforms in Higher Education
The widespread and rapid adoption of free Mobile Instant Messaging
(MIM) tools/platforms such as WhatsApp, Telegram, WeChat and Facebook
Messenger stems from their simplicity, ease of use and multi-modality
(i.e. video, audio, text) \cite{tang2017mobile}. Using these tools in
higher education institutions facilitates the delivery of personalized learning
that occurs anytime anywhere, and promotes collaborative learning
experiences and group discussions \cite{panah2020study}.
